Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-09-29 doc/JFLA2022/paper.tex
changes to the abstract

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library of commented proofs, developped under the \emph{Coq-Community} project.
  We present its evolution since a former presentation and how its structure is determined by other
  libraries and the \emph{Alectryon} literate proving tool.
\end{abstract}

>>>>

\begin{abstract}
  \emph{Hydra-battles} is a collaborative library on discrete math, written for the Coq proof assistant, and developped under the \emph{Coq-Community} project. The proof scripts are
  accompanied with an electronic book, made with the help of the \emph{Alectryon} litterate proving tool.
  We present the evolution of the mathematical contents since
  former presentations at JFLA meetings.
  Then, we show how the structure of the project is determined   by two  requirements which must continuously satisfied:
   maintenance of the library with respect to several Coq-Community projects it requires and evolutions of Coq, and 
  consistency of the book with respect to the library. 
\end{abstract}
